Demographic Groups with Stronger Biden Support in the Election Race

### 2024-04-05 paper/paper.qmd
update changes

The Cooperative Election Study (CES)conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases. The cases are based on the survey of adult pariticipants in 2022 fall. YouGov was commissioned to help the teams to conduct national sample surbey. They conducted the survey before and after elections. The first round survey were completed from September 29 to November 8, 2022 and the second period is gathered from November 10 to December 15, 2022. By offering an throughout views to different constituencies, voter demographics and voter behaviors, CES reveals the complexity of electoral behavior and voter demographics. By understanding voter behaviors,, we gain valuable insights that pave the way for refining and advancing democratic practices.

>>>>

The Cooperative Election Study [@main_data]conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases. The cases are based on the survey of adult pariticipants in 2022 fall. YouGov was commissioned to help the teams to conduct national sample surbey. They conducted the survey before and after elections. The first round survey were completed from September 29 to November 8, 2022 and the second period is gathered from November 10 to December 15, 2022. By offering an throughout views to different constituencies, voter demographics and voter behaviors, CES reveals the complexity of electoral behavior and voter demographics. By understanding voter behaviors,, we gain valuable insights that pave the way for refining and advancing democratic practices.
